---
title: "Assignment 5"
author: "Ruixuan Ma"
date: "9/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 5: Due Sunday, 23 September at 23:59PM
*For help with Rmarkdown for reports, see this [white paper](http://www.stat.cmu.edu/~cshalizi/rmarkdown/#math-in-r-markdown) from Carnegie Mellon University's Department of Statistics and Data Science.*

**I'm giving you some additional material to read. This should help you with the exercises I've assigned below.**


### Read About Lists
Read the following articles:

- [Basics of Lists](http://r4ds.had.co.nz/lists.html): read until you reach the **For loops vs functionals** subsection; you don't have to do the exercises at the end.
- [Editing Lists](https://www.datamentor.io/r-programming/list/): read entire article

Based on these lessons, here are some helpful definitions:

1. Subset a list by position or name with the `[` function
2. Subset a list by position or name and extract its *contents* with the `[[` function
3. Subset a list by name and extract its *contents* with the `$` function
3. Find the class of an object with the `class()` function.


### Examples
I will create a simple list, then I will subset it in all manner of ways. This is a `list` of one element, the `integer` 3 stored with name `a`.
```{r ex_list}
# Create the list
x_ls <- list(a = 3L, b = "five")

# What is x_ls?
class(x_ls)
```

#### The `[` Function
I can extract the first element of `x_ls` by name or position.
```{r subset1}
# Subset by name
x_ls["a"]

# What is returned by this?
class(x_ls["a"])


# Subset by position
x_ls[1]

# What is returned by this?
class(x_ls[1])
```

As we can see, the `[` function returns a list element. This can be helpful at times, but often we want the *contents* of that list element. The main upside to the `[` function is that we can select multiple list elements at once.
```{r subset1multiple}
x_ls[1:2]

# What is returned by this?
class(x_ls[1:2])
```

#### The `[[` Function
I can extract the contents of the first element of `x_ls` by name or position.
```{r subset2}
# Subset by name
x_ls[["a"]]

# What is returned by this?
class(x_ls[["a"]])


# Subset by position
x_ls[[1]]

# What is returned by this?
class(x_ls[[1]])
```

As we can see, the `[[` function returns the *contents* of the list element. We cannot, however, select multiple list elements with this function (try it yourself).

#### The `$` Function
I can extract the contents of the first element of `x_ls` by name only.
```{r subset3}
x_ls$a

# What is returned by this?
class(x_ls$a)
```

As we can see, the `$` function returns the *contents* of the list element. You might ask, "why do we need `$` when we have `[[`?" Notice that we didn't need to put `a` in quotes for `$` to work (`x_ls$a`, not `x_ls$"a"`). We will come back to the idea of using names of objects later this semester.


### Review
As a complimentary example to the pepper shaker, think about this list as a train. We can select the first car of the train with the `[` function. We could select any number of cars in the train with the `[` function. Additionally, we can extract the contents of a car by name or position with the `[[` function, but we can't select more than one car at a time. Finally, we can extract the contents of a train car by name with the `$` function; this function is special because it doesn't require us to type the quotes (`" "`) around the name.



## Exercises
1. Create a list with four elements:
    a. the character string `"Normal"` to represent the distribution
    b. a named vector of the population parameters
    c. a vector of 15 samples from a normal distribution with mean 2 and variance 5
    d. the components of a histogram of these samples
```{r}
n_ls <- list(
  DistributionName = "Normal",
  ParameterName = c(mean = 2, var = 5),
  n_sample = rnorm(15, 2, sqrt(5))
)

hist(n_ls$n_sample)

```
2. Print the distribution name and parameters (at the same time), and plot the saved histogram.
```{r}
n_ls[1:2]
plot(hist(n_ls$n_sample))
```
3. Print the summary and variance of this sample.
```{r}
summary(n_ls[[3]])
var(n_ls[[3]])
```
4. Test the hypothesis that these observations came from the distribution specified. Store the $p$-value, test statistic, critical value, and decision (reject or fail to reject) as new elements of the list.
```{r}
ttest_out <- t.test(
  x = n_ls$n_sample,
  alternative = "two.sided",
  mu = 2
)
names(ttest_out)
ttest_out$statistic
ttest_out$p.value
critVal <- qt(0.975, df = 15 - 1)
abs(ttest_out$statistic) > critVal
ttest_out$p.value < 0.05

# p-value
n_ls$pVal <- ttest_out$p.value

# test statistic
n_ls$testStat <- ttest_out$statistic

# critical value
n_ls$critVal <- critVal

# decision
n_ls$decision <- "Fail to Reject the Hypothesis that the True Mean Equals 2"

n_ls

```
5. Repeat this for the rest of the distributions we inspected in Assignment 4. Did you reject the null hypothesis for any of the distributions? If so, which ones. If so, why do you think you rejected the null hypothesis for these distributions? If not, why not?


# Binomial Distribution

```{r}
binom_ls <- list(
  dist   = "Binomial Distribution",
  params = c(mean = 6, var = 2),
  sample = rbinom(9, 5, 2/3)
)
hist(binom_ls$sample)

mean(binom_ls$sample)
var(binom_ls$sample)

cv_binom <- qt(0.975, 8)

ttest_binom <- t.test(
  binom_ls$sample,
  alternative = "two.sided",
  mu = 6
)

names(ttest_binom)

abs(ttest_binom$statistic) > cv_binom
ttest_binom$p.value < 0.05

binom_ls$pVal <- ttest_binom$p.value
binom_ls$teststat <- ttest_binom$statistic
binom_ls$cv <- cv_binom
binom_ls$decision <- "Reject the Hypothesis that the True Mean Equals 6"
```

# Poisson distribution
```{r}
pois_ls <- list(
  dist   = "Poisson Distribution",
  params = c(lambda = 3),
  sample = rpois(n = 15, lambda = 3)
)
  
hist(pois_ls$sample)

mean(pois_ls$sample)
var(pois_ls$sample)

cv_pois <- qt(0.975, 14)

ttest_pois <- t.test(
  pois_ls$sample,
  alternative = "two.sided",
  mu = 3
)

names(ttest_pois)

abs(ttest_pois$statistic) > cv_pois
ttest_pois$p.value < 0.05

pois_ls$pVal <- ttest_pois$p.value
pois_ls$teststat <- ttest_pois$statistic
pois_ls$cv <- cv_pois
pois_ls$decision <- "Fail to reject the Hypothesis that the True Mean Equals 3"
```


# Negative Binomial Distribution
```{r}
nbinom_ls <- list(
  dist   = "Negative Binomial Distribution",
  params = c(size = 5, prob = 0.5),
  sample = rbinom(15, 5, 0.5)
)
hist(nbinom_ls$sample)

mean(nbinom_ls$sample)
var(nbinom_ls$sample)

cv_nbinom <- qt(0.975, 14)

ttest_nbinom <- t.test(
  nbinom_ls$sample,
  alternative = "two.sided",
  mu = 5
)

names(ttest_nbinom)

abs(ttest_nbinom$statistic) > cv_nbinom
ttest_nbinom$p.value < 0.05

nbinom_ls$pVal <- ttest_nbinom$p.value
nbinom_ls$teststat <- ttest_nbinom$statistic
nbinom_ls$cv <- cv_nbinom
nbinom_ls$decision <- "Reject the Hypothesis that the True Mean Equals 5"
```

# Student t Distribution
```{r}
t_ls <- list(
  dist   = "Student t Distribution",
  params = c(nu = 4),
  sample = rt(15, 4, 0)
)
hist(t_ls$sample)

mean(t_ls$sample)
var(t_ls$sample)

cv_t <- qt(0.975, 14)

ttest_t <- t.test(
  t_ls$sample,
  alternative = "two.sided",
  mu = 0
)

names(ttest_t)

abs(ttest_t$statistic) > cv_t
ttest_t$p.value < 0.05

t_ls$pVal <- ttest_t$p.value
t_ls$teststat <- ttest_t$statistic
t_ls$cv <- cv_t
t_ls$decision <- "Fail to reject the Hypothesis that the True Mean Equals 0"
```

# Chi-Squared Distribution
```{r}
Chisq_ls <- list(
  dist   = "Chi-Squared Distribution",
  params = c(nu = 2),
  sample = rchisq(15, 2, 0)
)
hist(Chisq_ls$sample)

mean(Chisq_ls$sample)
var(Chisq_ls$sample)

cv_Chisq <- qt(0.975, 14)

ttest_Chisq <- t.test(
  Chisq_ls$sample,
  alternative = "two.sided",
  mu = 2
)

names(ttest_Chisq)

abs(ttest_Chisq$statistic) > cv_Chisq
ttest_Chisq$p.value < 0.05

Chisq_ls$pVal <- ttest_Chisq$p.value
Chisq_ls$teststat <- ttest_Chisq$statistic
Chisq_ls$cv <- cv_Chisq
Chisq_ls$decision <- "Fail to reject the Hypothesis that the True Mean Equals 2"
```

# F Distribution
```{r}
f_ls <- list(
  dist   = "F Distribution",
  params = c(n = 90, m = 12),
  sample = rf(15, 90, 12, 0)
)
hist(f_ls$sample)

mean(f_ls$sample)
var(f_ls$sample)

cv_f<- qt(0.975, 14)

ttest_f <- t.test(
  f_ls$sample,
  alternative = "two.sided",
  mu = 1.2
)

names(ttest_f)

abs(ttest_f$statistic) > cv_f
ttest_f$p.value < 0.05

f_ls$pVal <- ttest_f$p.value
f_ls$teststat <- ttest_f$statistic
f_ls$cv <- cv_f
f_ls$decision <- "Fail to reject the Hypothesis that the True Mean Equals 1.2"
```