---
title: "Assignment 4"
author: "Ruixuan Ma"
date: "9/14/2018"
output: html_document
---

```{r setup, include=FALSE}
set.seed(123)
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 4: Due Sunday, 16 September at 23:59PM
*For help with Rmarkdown for reports, see this [white paper](http://www.stat.cmu.edu/~cshalizi/rmarkdown/#math-in-r-markdown) from Carnegie Mellon University's Department of Statistics and Data Science.*

For each the seven statistical distributions we covered in the last assignment (Normal, Student's $t$, $\chi ^ 2$, $F$, Binomial, Negative Binomial, and Poisson), 

1. Generate and store a random vector of 10,000 observations, using the same parameters as the last homework:
    i. $N(\mu = 2, \sigma ^ 2 = 5 )$,
    ii. $t_{\nu = 4}$,
    iii. $\chi^2_{\nu = 2}$,
    iv. $F_{n = 90,\ m = 12}$,
    v. $Bin(n = 9, p = 2/3)$,
    vi. $NBin(n = 5, p = 1/2)$, and
    vii. $Pois(\lambda = 3)$.
```{r}
i <- rnorm(10000, 2, sqrt(5))
ii <- rt(10000, 4, 0)
iii <- rchisq(10000, 2, 0)
iv <- rf(10000, 90, 12, 0)
v <- rbinom(10000, 9, 2/3)
vi <- rnbinom(10000, 5, 0.5)
vii <- rpois(10000, 3)
```


2. Subset the first $N = 6$ values from the vector, and of this subset
    i. calculate the 5-Number Summary,
```{r}
summary(i[1:6])
summary(ii[1:6])
summary(iii[1:6])
summary(iv[1:6])
summary(v[1:6])
summary(vi[1:6])
summary(vii[1:6])
```
    ii. plot the histogram of the subset, and
```{r}
hist(i[1:6])
hist(ii[1:6])
hist(iii[1:6])
hist(iv[1:6])
hist(v[1:6])
hist(vi[1:6])
hist(vii[1:6])
```
    iii. plot the estimated density of this subset.
```{r}
plot(density(i[1:6]))
plot(density(ii[1:6]))
plot(density(iii[1:6]))
plot(density(iv[1:6]))
plot(density(v[1:6]))
plot(density(vi[1:6]))
plot(density(vii[1:6]))

```
3. Repeat Item 2 for the first $N =  10,\ 20,\ 30,\ \text{and}\ 50$ values from the random vector you generated in Item 1. Remark on the changing behaviour as the sample size increases. 
```{r}
summary(i[1:10])
summary(ii[1:10])
summary(iii[1:10])
summary(iv[1:10])
summary(v[1:10])
summary(vi[1:10])
summary(vii[1:10])

hist(i[1:10])
hist(ii[1:10])
hist(iii[1:10])
hist(iv[1:10])
hist(v[1:10])
hist(vi[1:10])
hist(vii[1:10])

plot(density(i[1:10]))
plot(density(ii[1:10]))
plot(density(iii[1:10]))
plot(density(iv[1:10]))
plot(density(v[1:10]))
plot(density(vi[1:10]))
plot(density(vii[1:10]))

summary(i[1:20])
summary(ii[1:20])
summary(iii[1:20])
summary(iv[1:20])
summary(v[1:20])
summary(vi[1:20])
summary(vii[1:20])

hist(i[1:20])
hist(ii[1:20])
hist(iii[1:20])
hist(iv[1:20])
hist(v[1:20])
hist(vi[1:20])
hist(vii[1:20])

plot(density(i[1:20]))
plot(density(ii[1:20]))
plot(density(iii[1:20]))
plot(density(iv[1:20]))
plot(density(v[1:20]))
plot(density(vi[1:20]))
plot(density(vii[1:20]))

summary(i[1:30])
summary(ii[1:30])
summary(iii[1:30])
summary(iv[1:30])
summary(v[1:30])
summary(vi[1:30])
summary(vii[1:30])

hist(i[1:30])
hist(ii[1:30])
hist(iii[1:30])
hist(iv[1:30])
hist(v[1:30])
hist(vi[1:30])
hist(vii[1:30])

plot(density(i[1:30]))
plot(density(ii[1:30]))
plot(density(iii[1:30]))
plot(density(iv[1:30]))
plot(density(v[1:30]))
plot(density(vi[1:30]))
plot(density(vii[1:30]))

summary(i[1:50])
summary(ii[1:50])
summary(iii[1:50])
summary(iv[1:50])
summary(v[1:50])
summary(vi[1:50])
summary(vii[1:50])

hist(i[1:50])
hist(ii[1:50])
hist(iii[1:50])
hist(iv[1:50])
hist(v[1:50])
hist(vi[1:50])
hist(vii[1:50])

plot(density(i[1:50]))
plot(density(ii[1:50]))
plot(density(iii[1:50]))
plot(density(iv[1:50]))
plot(density(v[1:50]))
plot(density(vi[1:50]))
plot(density(vii[1:50]))

# We can be infered from those density plots and histograms that the graph would become more smooth with sample size increasing.

```
4. Repeat Item 2 for the entire vector ($N = 10000$). For smaller values of $N$ from continuous distributions, which tool do you think gave a better representation of the full data: histogram or density plot? Did this change when you inspected the discrete distributions?
```{r}
summary(i)
summary(ii)
summary(iii)
summary(iv)
summary(v)
summary(vi)
summary(vii)

hist(i)
hist(ii)
hist(iii)
hist(iv)
hist(v)
hist(vi)
hist(vii)

plot(density(i))
plot(density(ii))
plot(density(iii))
plot(density(iv))
plot(density(v))
plot(density(vi))
plot(density(vii))

# For discrete distribution, histogram always be the good choice. But for continuous distribution, histogram is good for small size, density plot is good for for large size.

```
5. Contrast the 5-Number Summaries at each of the sample sizes (6, 10, 20, 30, 50, and 10000) for the skewed distributions vs. the symmetric distributions.
```{r}
# Comparing the 5-Number Summaries at each of the sample sizes for those distributions we can find that, for symmetric distribution, with the sample size increasing, the median and mean are getting closer. For skewed distribution, with the sample size increasing, the median become more far away from mean.
```