---
title: "assignment 1"
author: "Ruixuan Ma"
date: "8/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercises set 1
1. Create an object called "myAge" that holds your age *in months*. Hint: the multiplication operator in R is "*".
```{r}
myAge <- 23 * 12 + 9
```
2. Using the object "myAge", approximate the number of days you've been alive.Use 30.44 days per month. Check this against your age in days on WolframAlpha. How many days off was your estimate?
```{r}
myAge <- 23 * 12 * 30.44 + 10 * 30.44 +3
```
3. Using the object "myAge", find your decimal age. (Hint: the division operator is "/".)
```{r}
myAge <- (23 * 12 * 30.44 + 10 * 30.44 +3)/365
```
4. Copy and Paste MyAge into the console and press ENTER. What happens? Why?
# The console display error: object 'MyAge' no found. Because for R language, myAge and MyAge are not the same thing.



# Exercises set 2

1. Five people start the newest diet craze. Their weights (in kg) before and after were [78 72 78 79 105] and [67 65 79 70 93], respectively. Store these two vectors as "wtBefore" and   "wtAfter", respectively. Find the total weight lost, the average weight lost, and the weight lost per person. Hint: see the ?sum and ?mean functions.
```{r}
wtBefore <- c(78, 72, 78, 79, 105)
wtAfter <- c(67, 65, 79, 70, 93)
sum(78, 72, 78, 79, 105) - sum (67, 65, 79, 70, 93)
(sum(78, 72, 78, 79, 105) - sum (67, 65, 79, 70, 93))/5
78-67
72-65
78-79
79-70
105-93
```
2. Create the following vectors using the rep() and seq() functions:
   a) the first non-negative integer powers of 2
```{r}
0^2
   
```
   b) 1, 1.5, 2, 2.5, ..., 12
```{r}
seq(from = 1, to = 12, by = 0.5)
```
   c) 1, 8, 27, 64, ..., 1000
```{r}
i <- seq(from = 1, to = 10, by = 1)
i^3
```
   d) 1, -1/2, 1/3, -1/4, ..., -1/100
```{r}
i <- seq(from = 1, to = 100, by = 1)
p <- (-1)^i
-p / i
```
   e) 1, 0, 3, 0, 5, 0, 7, 0, ..., 0, 49
```{r}
rep(1:0, length.out = 49) * (1:49)
```
   f) 1, 3, 6, 10, 15, ..., 210 (Hint: ?cumsum)
```{r}
cumsum(1:20)
```
   g) 1, 2, 2, 3, 3, 3, ..., 10, 10, 10, 10, 10, 10, 10, 10, 10, 10 (Hint: ?rep)
```{r}
i <- seq(from = 1, to = 10, by = 1)
rep(1:10, times = i)
```
   
   
3. (ADVANCED) The jth term of the Taylor-MacLaurin series for the natural logarithm is $$ log(1 - x) := - \lim_{n \to \infty} \sum \limits_{j = 1}^n \frac{x ^ j}{j}.
$$ Find the residuals of this approximation for n = 5, 10, 50, 100 around x = 0.25
```{r}
n<-5
for (j in 1:n){
a<-sum(0.25^j/j)+log(1-0.25)
}

n<-10
for (j in 1:n){
b<-(log(1-0.25) + sum(0.25^j/j))
}

n<-50
for (j in 1:n){
c<-(log(1-0.25) + sum(0.25^j/j))
}

n<-100
for (j in 1:n){
d<-(log(1-0.25) + sum(0.25^j/j))
}
```
# Exercises set 3

 1. Create a vector of the months of the year and store it in an object called "mons".
```{r}
mons <- c("January", "February", "March", "April", "May", "June", "July", "August", "September", "Octomber", "November", "December")
```
 2. You would like to discard the first three months, so you type "mons[-1:3]".
    What happened? Why should you type instead?
```{r}
# It shows error in this code
# we should type 
mons[-c(1, 2, 3)]
```
 3. Find a method to use the "length()" function to find the last four entries
    of *any* atomic vector. Apply this to find the last four months of the
    year.
```{r}
mons[seq(from = length(mons)-3, to = length(mons), by = 1)]
```
 4. Logically subset the uppercase vector of English letters in the following
    ways:
    a) Type LETTERS and press ENTER. What is your guess to find the lower case
       letters?
```{r}
# type letters and press ENTER
```
    b) Create a vector of the first 12 upper-case English letter
```{R}
LETTERS[1:12]
```
    c) Create a vector of the 1st, 3rd, 5th, 7th, ..., 25th English letters
```{r}
LETTERS[seq(1, 25, by = 2)]
LETTERS[seq(2, 26, by = 2)]

```
    d) Create a vector of the consonants. (Hint: it may be easier to find the
       letters that are *not* one of the vowels)
```{r}
LETTERS[c(2,3,4,6,7,8,10,11,12,13,14,16,17,18,19,20,22,23,24,25,26)]

# or

randLetter <- LETTERS
randLetter %in% c("A", "E", "I", "O", "U")
isVowel <- LETTERS %in% c("A", "E", "I", "O", "U")
LETTERS[isVowel]
LETTERS[!isVowel]
```
