---
title: "Assignment 6"
author: "Ruixuan Ma"
date: "9/27/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 5: Due Sunday, 30 September at 23:59PM
*For help with Rmarkdown for reports, see this [white paper](http://www.stat.cmu.edu/~cshalizi/rmarkdown/#math-in-r-markdown) from Carnegie Mellon University's Department of Statistics and Data Science.*

### Part 1
Finish the work you have left over from Assignment 4. Email me when you finish, so I can look at it. Please finish this by Tuesday evening.

### Part 2
Read [this article](https://www.r-bloggers.com/5-ways-to-subset-a-data-frame-in-r/) and execute the code in it. For the last example in this article (using the `dplyr` package), use the `tidyverse` package you just installed instead. The `filter()` and `select()` functions are the same. Include the code from this article and your output as the first section of your markdown report.
### import education expenditure data set and assign column names
```{r}
education <- read.csv("https://vincentarelbundock.github.io/Rdatasets/csv/robustbase/education.csv", stringsAsFactors = FALSE)
colnames(education) <- c("X","State","Region","Urban.Population","Per.Capita.Income","Minor.Population","Education.Expenditures")
View(education)

ed_exp1 <- education[c(10:21),c(2,6:7)]

ed_exp2 <- education[-c(1:9,22:50),-c(1,3:5)]

ed_exp3 <- education[which(education$Region == 2),names(education) %in% c("State","Minor.Population","Education.Expenditures")]

ed_exp4 <- subset(education, Region == 2, select = c("State","Minor.Population","Education.Expenditures"))

install.packages("tidyverse")
library(tidyverse)
ed_exp5 <- select(filter(education, Region == 2),c(State,Minor.Population:Education.Expenditures))
```


### Part 3
1. Create the `myClass` data frame we covered in class. When you create the data frame, make sure that your character **strings** are not changed to **factors** (look at `?data.frame` for the `stringsAsFactors` argument; also look at how the article does it). Include a row in the data frame for me, you, and your classmates. Here are the features to measure:
    a. last name
    b. first name
    c. number of cups of coffee or tea per day, and
    d. current neighbourhood
```{r}
myClass <- data.frame(
   Surname = c("Odom", "Ma", "Dyatchenko", "Gmunder"),
   GivenName = c("Gabriel", "Ruixuan", "Nina", "Kristin"),
   CupsCoffeeTea = c(0, 2, 3, 0),
   neighbourhood = c("Pembroke Pines", "Modera Riverhouse", "Miami Beach", "Brickell")
)
```
2. For each of the five data-frame subsetting methods in the article above, subset
    i. Your row
```{r}
myRow1 <- myClass[2,c(1:4)]
myRow2 <- myClass[-c(1,3:4),c(1:4)]
myRow3 <- myClass[which(myClass$Surname == "Ma"),names(myClass) %in% c("Surname","GivenName","CupsCoffeeTea","neighbourhood")]
myRow4 <- subset(myClass, Surname == "Ma", select = c("Surname","GivenName","CupsCoffeeTea","neighbourhood"))
myRow5 <-select(filter(myClass, Surname == "Ma"),c(Surname:neighbourhood))
```
    ii. the column of neighbourhoods
```{r}
col_nbh1 <- myClass[c(1:4),4]
col_nbh2 <- myClass[c(1:4),-c(1:3)]
col_nbh3 <- myClass[names(myClass) %in% "neighbourhood"]
col_nbh4 <- subset(myClass, select = "neighbourhood")
col_nbh5 <- select(myClass, neighbourhood)
```
    iii. your current neighbourhood
```{r}
my_nbh1 <- myClass[2,4]
my_nbh2 <- myClass[-c(1,3:4),-c(1:3)]
my_nbh3 <- myClass[which(myClass$Surname == "Ma"),names(myClass) %in% c("neighbourhood")]
my_nbh4 <- subset(myClass, Surname== "Ma", select = "neighbourhood")
my_nbh5 <- select(filter(myClass, Surname == "Ma"), "neighbourhood")
```
    iv. your AND my current neighbourhood, as a data frame
```{r}
yandm_nbh1 <- myClass[c(1:2),4]
yandm_nbh2 <- myClass[-c(3:4),-c(1:3)]
yandm_nbh3 <- myClass[which(myClass$Surname == c("Odom","Ma")),names(myClass) %in% c("neighbourhood")]
yandm_nbh4 <- subset(myClass, Surname== c("Odom","Ma"), select = "neighbourhood")
yandm_nbh5 <- select(filter(myClass, Surname == c("Odom","Ma")),c(neighbourhood))
```
    v. the rows with people who drink coffee or tea
```{r}
drink1 <- myClass[c(2:3),c(1:4)]
drink2 <- myClass[-c(1,4),c(1:4)]
drink3 <- myClass[which(myClass$Surname == c("Dyatchenko","Ma")),names(myClass) %in% c("Surname","GivenName","CupsCoffeeTea","neighbourhood")]
drink4 <- subset(myClass, Surname== c("Dyatchenko","Ma"), select = c("Surname","GivenName","CupsCoffeeTea","neighbourhood"))
drink5 <- select(filter(myClass, Surname == c("Dyatchenko","Ma")),c(Surname:neighbourhood))
```
    vi. the neighbourhoods of people who *do not* drink coffee or tea
```{r}
NoDrink1 <- myClass[c(1,4),4]
NoDrink2 <- myClass[-c(2:3),-c(1:3)]
NoDrink3 <- myClass[which(myClass$Surname == c("Odom","Gmunder")),names(myClass) %in% c("neighbourhood")]
NoDrink4 <- subset(myClass, Surname== c("Odom","Gmunder"), select = "neighbourhood")
NoDrink5 <- select(filter(myClass, Surname == c("Odom","Gmunder")),c(neighbourhood))

```